### 2022-05-11 supplement.Rmd

# Re-run the jackknife analysis only if requested
jackknife_file <- here(tables_dir, "jackknife.csv")
if (run$jackknife_analysis) {

  # Re-fit the meta-analysis, leaving one experiment out at a time
  # Using parallelization with `furrr`
  n_cores <- availableCores()
  n_workers <- n_cores %/% n_chains
  plan(multisession, workers = n_workers)
  future_map_dfr(seq_len(nrow(dat)), function(jackknife_index) {
    dat_jackknife <- dat[-jackknife_index, ]
    res_jackknife <- update(res_brm, newdata = dat_jackknife, refresh = 0)
    print_res_table(
      res_jackknife,
      label_1 = dat$article[jackknife_index],
      label_2 = dat$group_long[jackknife_index],
      label_col_1 = "Article", label_col_2 = "Experiment"
    )
  }) -> jackknife_tab

  # Save the table
  write_csv(jackknife_tab, file = jackknife_file)
} else {

  # Otherwise we load the pre-computed results
  jackknife_tab <- read_csv(jackknife_file, col_types = "c")
}

# Display the table
apa_table(
  jackknife_tab,
  align = "llcccc",
  caption = "Jackknife (leave-one-out) analysis",
  font_size = "scriptsize",
  escape = FALSE
)
```

```{r, sensitivity_analysis}
# Re-run the sensitivity analyses only if requested
if (run$sensitivity_analysis) {

@@

      # Return both as a tibble together with the label
      return(
        tibble(
          manipulation_value = str_c("$r = ", print_num(ri_sens), "$"),
          res = list(res),
          res_reg = list(res_reg),
        )
      )
    }) %>%
    bind_cols(
      manipulation_name = c("Assumed correlation", rep("", nrow(.) - 1)), .
    ) -> res_ri_sens

@@

      # Return both as a tibble together with the label
      return(
        tibble(
          manipulation_value = prior_name,
          res = list(res),
          res_reg = list(res_reg),
          res_gender = list(res_gender)
        )
      )
    }) %>%
    bind_cols(
      manipulation_name = c("Prior specification", rep("", nrow(.) - 1)), .
    ) -> res_prior_sens

  # Combine results from all sensitivity analyses
  res_sens <- bind_rows(res_ri_sens, res_prior_sens)

  # Backup for reuse
  saveRDS(res_sens, here(models_dir, "res_sens.rds"))
} else {
  # Otherwise we load the pre-fitted models
  res_sens <- readRDS(here(models_dir, "res_sens.rds"))
}
```

\renewcommand{\arraystretch}{1.0}

```{r, tabs5, include=TRUE}
# Combine results for the (main) meta-analysis of mental rotation performance
tab_sens <- res_sens %>%
  select(res, manipulation_name, manipulation_value) %>%
  pmap_dfr(function(res, manipulation_name, manipulation_value) {
    print_res_table(
      res,
      label_1 = manipulation_name, label_2 = manipulation_value,
      label_col_1 = "Manipulation", label_col_2 = " "
    )
  })

# Display the table
apa_table(
  tab_sens,
  caption = "Sensitivity analyses for the meta-analysis of mental rotation performance",
  font_size = "scriptsize", escape = FALSE
)

# Save the table
write_csv(tab_sens, file = here(tables_dir, "tabs5_sens.csv"))
```

```{r, tabs6, include=TRUE}
# Helper functions for printing results as a table
print_res_reg_table <- function(res_reg,
                                label_1,
                                label_2,
                                label_col_1,
                                label_col_2) {
  spread_draws(res_reg, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
    transmute(
      `Intercept` = b_Intercept,
      `Female - mixed` = b_gender2M1,
      `Male - female` = b_gender3M2,
      `Age (per year)` = b_age_c,
      `Habituation - VoE` = b_task2M1,
      `[Female - mixed] $\\times$ age` = `b_gender2M1:age_c`,
      `[Male - female] $\\times$ age` = `b_gender3M2:age_c`
    ) %>%
    summarize(across(.fns = mean_qi)) %>%
    map_dfc(~ print_ci(.$ymin, .$ymax, mean = .$y)) -> tab
  if (!is.null(label_2)) {
    label_2_tab <- tibble(tmp = c(label_2, rep(NA, nrow(tab) - 1))) %>%
      rename(!!label_col_2 := tmp)
    tab <- cbind(label_2_tab, tab)
  }
  if (!is.null(label_1)) {
    label_1_tab <- tibble(tmp = c(label_1, rep(NA, nrow(tab) - 1))) %>%
      rename(!!label_col_1 := tmp)
    tab <- cbind(label_1_tab, tab)
  }
  return(tab)
}

# Combine results for the meta-regression of mental rotation performance
tab_sens_reg <- res_sens %>%
  select(
    res_reg, manipulation_name, manipulation_value
  ) %>%
  pmap_dfr(function(res_reg, manipulation_name, manipulation_value) {
    print_res_reg_table(
      res_reg,
      label_1 = manipulation_name, label_2 = manipulation_value,
      label_col_1 = "Manipulation", label_col_2 = " "
    )
  })

# Display the table
apa_table(
  tab_sens_reg,
  caption = "Sensitivity analyses for the meta-regression of mental rotation performance",
  font_size = "scriptsize", landscape = TRUE, escape = FALSE
)

# Save the table
write_csv(tab_sens_reg, file = here(tables_dir, "tabs6_sens_reg.csv"))
```

```{r, tabs7, include=TRUE}
# Combine results for the meta-analysis of gender differences
tab_sens_gender <- res_sens %>%
  filter(!map_lgl(res_gender, is.null)) %>%
  select(res_gender, manipulation_name, manipulation_value) %>%
  pmap_dfr(function(res_gender, manipulation_name, manipulation_value) {
    print_res_table(
      res_gender,
      label_1 = manipulation_name, label_2 = manipulation_value,
      label_col_1 = "Manipulation", label_col_2 = " "
    )
  })

# Display the table
apa_table(
  tab_sens_gender,
  caption = "Sensitivity analyses for the meta-analysis of gender differences",
  font_size = "scriptsize", escape = FALSE
)

# Save the table
write_csv(tab_sens_gender, file = here(tables_dir, "tabs7_sens_gender.csv"))
```

>>>>

# Re-run the jackknife analysis only if requested
if (run$jackknife_analysis) {

  # Re-fit the meta-analysis, leaving one experiment out at a time
  # Using parallelization with `furrr`
  n_cores <- availableCores()
  n_workers <- n_cores %/% n_chains
  plan(multisession, workers = n_workers)
  future_map_dfr(seq_len(nrow(dat)), function(jackknife_index) {
    dat_jackknife <- dat[-jackknife_index, ]
    res_jackknife <- update(res_brm, newdata = dat_jackknife, refresh = 0)
    print_res_table(
      res_jackknife,
      label_1 = dat$article[jackknife_index],
      label_2 = dat$group_long[jackknife_index],
      label_col_1 = "Article", label_col_2 = "Experiment"
    )
  }) -> tab_jackknife

  # Save the table
  write_csv(tab_jackknife, file = here(tables_dir, "jackknife.csv"))
} else {

  # Otherwise we load the pre-computed results
  tab_jackknife <- read_csv(
    here(tables_dir, "jackknife.csv"),
    col_types = "c", na = character()
  )
}

# Display the table
apa_table(
  tab_jackknife,
  align = "llcccc",
  caption = "Jackknife (leave-one-out) analysis",
  font_size = "scriptsize",
  escape = FALSE
)
```

```{r, sensitivity_analysis, include=TRUE}
# Helper functions for printing results as a table
print_res_reg_table <- function(res_reg,
                                label_1,
                                label_2,
                                label_col_1,
                                label_col_2) {
  spread_draws(res_reg, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
    transmute(
      `Intercept` = b_Intercept,
      `Female - mixed` = b_gender2M1,
      `Male - female` = b_gender3M2,
      `Age (per year)` = b_age_c,
      `Habituation - VoE` = b_task2M1,
      `[Female - mixed] $\\times$ age` = `b_gender2M1:age_c`,
      `[Male - female] $\\times$ age` = `b_gender3M2:age_c`
    ) %>%
    summarize(across(.fns = mean_qi)) %>%
    map_dfc(~ print_ci(.$ymin, .$ymax, mean = .$y)) -> tab
  if (!is.null(label_2)) {
    label_2_tab <- tibble(tmp = c(label_2, rep(NA, nrow(tab) - 1))) %>%
      rename(!!label_col_2 := tmp)
    tab <- cbind(label_2_tab, tab)
  }
  if (!is.null(label_1)) {
    label_1_tab <- tibble(tmp = c(label_1, rep(NA, nrow(tab) - 1))) %>%
      rename(!!label_col_1 := tmp)
    tab <- cbind(label_1_tab, tab)
  }
  return(tab)
}

# Re-run the sensitivity analyses only if requested
if (run$sensitivity_analysis) {

@@

      # Return both as a tibble together with the label
      return(
        tibble(
          manipulation_value = str_c("$r = ", print_num(ri_sens), "$"),
          res = list(res),
          res_reg = list(res_reg),
        )
      )
    }) %>%
    bind_cols(
      manipulation_name = c("Assumed correlation", rep("", nrow(.) - 1)), .
    ) -> sens_ri

@@

      # Return both as a tibble together with the label
      return(
        tibble(
          manipulation_value = prior_name,
          res = list(res),
          res_reg = list(res_reg),
          res_gender = list(res_gender)
        )
      )
    }) %>%
    bind_cols(
      manipulation_name = c("Prior specification", rep("", nrow(.) - 1)), .
    ) -> sens_prior

  # Combine results from all sensitivity analyses
  sens <- bind_rows(sens_ri, sens_prior)

  # Create table for the (main) meta-analysis of mental rotation performance
  sens %>%
  select(res, manipulation_name, manipulation_value) %>%
  pmap_dfr(function(res, manipulation_name, manipulation_value) {
    print_res_table(
      res,
      label_1 = manipulation_name, label_2 = manipulation_value,
      label_col_1 = "Manipulation", label_col_2 = " "
    )
    }) -> tab_sens
  write_csv(tab_sens, file = here(tables_dir, "sens.csv"))

  # Create table for the meta-regression of mental rotation performance
  sens %>%
  select(
    res_reg, manipulation_name, manipulation_value
  ) %>%
  pmap_dfr(function(res_reg, manipulation_name, manipulation_value) {
    print_res_reg_table(
      res_reg,
      label_1 = manipulation_name, label_2 = manipulation_value,
      label_col_1 = "Manipulation", label_col_2 = " "
    )
    }) -> tab_sens_reg
  write_csv(tab_sens_reg, file = here(tables_dir, "sens_reg.csv"))

  # Create table for the meta-analysis of gender differences
  sens %>%
  filter(!map_lgl(res_gender, is.null)) %>%
  select(res_gender, manipulation_name, manipulation_value) %>%
  pmap_dfr(function(res_gender, manipulation_name, manipulation_value) {
    print_res_table(
      res_gender,
      label_1 = manipulation_name, label_2 = manipulation_value,
      label_col_1 = "Manipulation", label_col_2 = " "
    )
    }) -> tab_sens_gender
  write_csv(tab_sens_gender, file = here(tables_dir, "sens_gender.csv"))
} else {

  # Otherwise we load the pre-computed results
  tab_sens <- read_csv(
    here(tables_dir, "sens.csv"),
    col_types = "c", na = character(), trim_ws = FALSE
  )
  tab_sens_reg <- read_csv(
    here(tables_dir, "sens_reg.csv"),
    col_types = "c", na = character(), trim_ws = FALSE
  )
  tab_sens_gender <- read_csv(
    here(tables_dir, "sens_gender.csv"),
    col_types = "c", na = character(), trim_ws = FALSE
  )
}

# Display the tables
apa_table(
  tab_sens,
  caption = "Sensitivity analyses for the meta-analysis of mental rotation performance",
  font_size = "scriptsize", escape = FALSE
)
apa_table(
  tab_sens_reg,
  caption = "Sensitivity analyses for the meta-regression of mental rotation performance",
  font_size = "scriptsize", landscape = TRUE, escape = FALSE
)
apa_table(
  tab_sens_gender,
  caption = "Sensitivity analyses for the meta-analysis of gender differences",
  font_size = "scriptsize", escape = FALSE
)
```
